\section*{Overview}

This module contains two thematic areas; one focuses on big questions
for politics in a world of rapidly changing technologies,
globalization, migration, and challenges to democracy. The other looks
at major policy problems (e.g, development, the Energiewende, Resource
depletion, and sustainable development) and how they are being
addressed by governments, industrial actors, and civil society.

The module is intended as an introduction to the questions and
research being addressed in the main thematic areas of the master's
program: big transformations and their environmental, technological,
and social dimensions; sustainability and democracy in a digital age;
and global governance, ethics and technology. The links between these
areas and research areas found in the TUM, such as economics and
policy, digital technologies, social responsibility and corporate
governance, and urbanization, mobility, and energy will be explained.

\textbf{Note} that this document is intended as a cram-sheet summary
of the course for last-minute reading. It is not comprehensive and
generally leaves out case studies that we looked at during the course
(development in Africa, Bees, Geothermal Energy, AI, etc), instead
aiming to include some of the more general principles and theories
that we've covered.

\section*{Attribution}

These notes are based off of the readings and lecture slides from the
course. I was unable to include links to the relevant readings or
lecture slides, but if you look on Moodle they should be fairly easy
to find.

\section*{Contribution}

Pull requests are very welcome:
\url{https://git.sr.ht/~todd/University/tree/master/POL40100/review-notes}
